Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
acks

\begin{ack}
  We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347. 
  Additionally, this material is based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No. 2040434. \jessie{confirm GRFP number}
\end{ack}

>>>>

\begin{ack}
  We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347 and Graduate Research Fellowship No.\ 2040434.
\end{ack}
